%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Original Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.325in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{0.875in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\def\ifempty#1{\def\temp{#1}\ifx\temp\empty}

\newcommand{\resumeItem}[2]{
  \item\small{
    \ifempty{#1}#2\else\textbf{#1}{: #2\vspace{-2pt}}\fi
  }
}

% ~ on each side of \hfill guarantees a literal space in the PDF text layer
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \textbf{#1}~\hfill~#2 \\
    \textit{\small#3}~\hfill~\textit{\small#4}
  \vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \textit{\small#1}~\hfill~\textit{\small#2}
    \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
  \textbf{\Large Mykola Nechyporuk } & \href{mailto:io@mykola.cc}
  {io@mykola.cc}
  & \href{https://www.github.com/MechyKola}{github.com/MechyKola}\\
  London/Stockholm & +44 7413766103 & \href{https://www.linkedin.com/in/mykolan}
  {linkedin.com/in/mykolan}\\
  
\end{tabular*}


%--------SUMMARY------------
\section{Summary}
  {Full stack software engineer with 4+ years in cross functional, compliance heavy environments, turning ambiguous regulatory requirements into efficient, reliable, and developer friendly systems.} \\


%--------SKILLS------------
\section{Skills}
  \textbf{Languages}{ Javascript, Hack(PHP), Erlang, SQL, Python, Go, C\#, Java, C} \\
  \textbf{Technologies}{ ReactJS, GraphQL, Vue.js, WPF, Git, Mercurial} \\


%-----------TECHNICAL-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Meta (WhatsApp)}{London, UK}
      {IC4 Software Engineer}{Feb. 2024 - Current}
      \resumeItemListStart
      	\resumeItem{}
          {Led design and rollout of an offline code-analysis platform to inventory operational loggers across the codebase, creating a reliable source of truth for compliance and observability.}
        \resumeItem{}
          {Enabled static and dynamic analysis pipelines and CI integration that tracks privacy assignment of loggers, fulfilling EU regulatory commitments while preserving developer velocity.}
        \resumeItem{}
          {Introduced ownership attribution for operational logging, enabling targeted task delegation and reducing load on critical infra oncall rotations.}
        \resumeItem{}
          {Owned and evolved an internal data-access tool, aligning engineering and approval stakeholders on streamlined workflows and onboarding multiple engineers to operate and extend it.}
      	\resumeItem{}
          {Onboarded legacy metric identifiers into automated deletion systems, eliminating redundant storage and saving \$40k+ per year while simplifying data-retention compliance.}
        \resumeItem{}
          {Implemented dozens of updates to production services to improve tracking of data flows within and between systems, working with service owners to roll out changes safely.}
        \resumeItem{}
          {Optimised critical compliance pipelines (time, space, and DB connection usage), improving reliability and lowering operational costs for regulatory reporting.}
      \resumeItemListEnd
      \resumeSubSubheading
      {IC3 Software Engineer}{May. 2022 - Feb. 2024}
      \resumeItemListStart
        \resumeItem{}
          {Scoped and delivered a tool to track data access requiring legal approval, partnering with legal and engineering stakeholders to automate work that previously consumed an entire team.}
        \resumeItem{}
          {Reduced time to access by over 90\% by designing automated notifications and parallelising stakeholder approvals.}
        \resumeItem{}
          {Structured previously freeform access records into auditable, schematised data, enabling faster internal audits and simplifying regulatory reporting.}
        \resumeItem{}
          {Initiated and organised team and office-wide social events (swag, dinners, activities), strengthening cohesion and supporting onboarding of new colleagues.}
      \resumeItemListEnd
    \resumeSubheading
      {Optiver}{Amsterdam, NL}
      {Software Engineer Intern}{Jul. 2021 - Aug. 2021}
      \resumeItemListStart
      	\resumeItem{}
          {Owned requirements gathering, design, and implementation of a C\# WPF GUI to navigate 2M+ data feeds.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Bristol}{Bristol, UK}
      {Teaching Assistant}{Oct. 2020 - May. 2021}
      \resumeItemListStart
      	\resumeItem{}
          {Taught Imperative Programming (C), Mathematics for Computer Science A, and Algorithms I.}
      \resumeItemListEnd
    \resumeSubheading
      {Commerzbank AG}{London, UK}
      {Software Engineering Intern}{Jun. 2020 - Sep. 2020}
      \resumeItemListStart
      	\resumeItem{}
          {Owned and developed a CRUD frontend and a full-stack log monitor (React, Go, WebSockets) for live metrics.}
      \resumeItemListEnd
    \resumeSubheading
      {Oxford Economics}{Oxford, UK}
      {Software Development Intern}{Jul. 2018 - Aug. 2018}
      \resumeItemListStart
      	\resumeItem{}
          {Developed C\# chatbot for requesting and viewing economic reports in chat.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Bristol}{Bristol, UK}
      {BSc (Hons) Computer Science}{2019 - 2022}
      \resumeItemListStart
      	\resumeItem{}
          {President of the University of Bristol Computer Science Society: 20+ events with up to 100+ attendees.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  
%-------------------------------------------
\end{document}
